Under-approximation of reachability in multivalued asynchronous networks

### 2013-04-02 parts/sa.tex
proofreading of section 3

The reachability of a process $a_i$ of a sort $a$ from another process $a_j$ is called an objective and is denoted $\PHobjp{a}{j}{i}$ (\pref{def:obj}).
\begin{definition}[Objective ($\Obj$)]
\label{def:obj}
  If $a \in \components$, the reachability of a process $a_j$ from a process $a_i$ is called an \emph{objective}, noted $\PHobj{a_i}{a_j}$.
  The set of all objectives is called $\Obj \DEF \{ \PHobj{a_i}{a_j} \mid a \in \components \wedge (a_i, a_j) \in \PHl_a^2 \}$.
  For an objective $P = \PHobj{a_i}{a_j} \in \Obj$, we define: $\PHsort(P) = a$, $\PHtarget(P)=a_i$, $\PHbounce(P)=a_j$,
  and $P$ is \emph{trivial} if $a_i = a_j$.
\end{definition}
\noindent
We define an \emph{objective sequence} as a sequence of objectives in which each objective target must be equal to the previous objective bounce of the same sort, if it exists.
The set of all objective sequences is denoted by $\OS$.

A context (\pref{def:context}) is an extension of the notion of state that can stand for a set of possible initial states.
We also extend the override operator to a context and a set of processes (\pref{def:ctxcap}).
\begin{definition}[Context ($\Ctx$)]
\label{def:context}
  A \emph{context} $\ctx$ associates to each sort in $\PHs$ a non-empty subset of its processes:
  $\forall a \in \PHs, \PHget{\ctx}{a} \subseteq \PHl_a \wedge \PHget{\ctx}{a} \neq \emptyset$.
  $\Ctx$ is the set of all contexts.
\end{definition}
%
\begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \rightarrow \Ctx$]
\label{def:ctxcap}
  For a given context $\ctx\in\Ctx$ and a set of processes $ps \in \powerset(\PHproc)$,
  the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by:
  \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} =
  \begin{cases}
    \{ p \in ps \mid \PHsort(p)=a \} & \text{if } \exists p \in ps, \PHsort(p)=a,\\
    \PHget{\ctx}{a} & \text{else.}
  \end{cases}
  \]
\end{definition}
\noindent
For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
$\exists s \subseteq \ctx, \delta \in \Sce(s)$.
We denote then: $\delta \in \Sce(\ctx)$,
%$\supp(\delta) \subseteq \ctx$. 
and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
where $\ceil(\delta)$ is the set containing the last process (hitter or bounce) of each sort present in $\delta$.

@@

Finally, bounce sequences on a sort $a$ (\pref{def:bs}) are sequences of actions hitting $a$ in which the bounce process of each action is the hitter process of the following action.
Bounce sequences are used to find sequences of actions that locally solve a given objective.
%solve an objective locally, by finding the sequences of actions that allow to reach a process.
A bounce sequence can be abstracted into its sets of hitters that are not in sort $a$.
%of every action that are different from the considered sort (\pref{def:aBS}).
This abstraction allows to propagate an objective into objectives on other sots.
In the following, we denote: $\Sol = \powerset(\PHproc)$.
\begin{definition}[Bounce sequence ($\BS$)]
\label{def:bs}
  A \emph{bounce sequence} $\zeta$ is a sequence of actions so that $\forall n \in \indexes{\zeta}, n < |\zeta|, \PHbounce(\zeta_{n}) = \PHtarget(\zeta_{n+1})$.
  $\BS$ denotes the set of all bounce sequences, and
  $\BS(P)$ denotes the set of bounce sequences \emph{solving} an objective $P$:
  \[
    \BS(\PHobj{a_i}{a_j}) = \{ \zeta \in \BS \mid \PHtarget(\zeta_1)= a_i \wedge \PHbounce(\zeta_{|\zeta|}) = a_j \} \enspace.
  \]
  Obviously, $\emptyseq \in \BS(\obj{a_i}{a_i})$; and $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$.
\end{definition}
%
\begin{definition}[$\aBS:\Obj \mapsto \powerset(\Sol)$]
\label{def:aBS}
  \[
    \aBS(P) = \{ \abstr{\zeta} \in \Sol \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \abstr{\zeta'} \subsetneq \abstr{\zeta} \} \enspace,
  \]
  where $\abstr{\zeta} = \{ \PHhitter(\zeta_n) \mid  n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$.
\end{definition}

@@

We define $\concr(\w)$ as the set of scenarios concretising an objective sequence $\w$ in the context $\ctx$.
In \pref{def:uconcr}, we define $\uconcr(\w)$ as equal to $\concr(\w)$ if and only if $\concr(\w)$ contains scenarios starting from all states $s \subseteq \ctx$.
\pref{th:uconcr-ctx} will be used to over-approximate the initial context $\ctx$.
%if such a scenario exists in all states $s \subseteq \ctx$.
%
\begin{comment}
\begin{definition}[$\concr: \OS \mapsto \powerset(\Sce)$]
\label{def:concr}
\towrite{Simplifier ? Supprimer la def formelle ?}
  For a given $\w \in \OS$, $\concr(\w)$ is the set of scenarios concretising $\w$ in the context $\ctx$:
  \begin{align*}
    \concr(\w) = \{ \delta \in \Sce \mid & (\w^\vartriangle = \emptyseq \wedge \delta = \emptyseq) 
      \vee (\w^\vartriangle \neq \emptyseq \wedge \supp(\delta) \subseteq \ctx
    \\ &
      \wedge \exists \phi:\indexes{\w} \mapsto \indexes{\delta}, (\forall n, m \in \indexes{\w}, n < m \Leftrightarrow \phi(n) \leq \phi(m)) 
    \\ &
      \wedge \forall n \in \indexes{\w}, \PHbounce(\w_n) \in \ctx \PHplay \delta_{1..\phi(n)})
    \}
    \enspace,
  \end{align*}
  where $\omega^\vartriangle$ refers to the sequence of objectives $\omega$ where the trivial objectives have been removed.
\end{definition}
%
\begin{definition}[$\concr: \powerset(\OS) \mapsto \powerset(\Sce)$]
\label{def:concr-set}
  $\concr(\W) = \{ \delta \in \concr(\w) \mid \w \in \W \} \enspace.$
\end{definition}
\end{comment}
%
\begin{definition}[$\uconcr: \OS \mapsto \powerset(\Sce)$]
\label{def:uconcr}
  \[
  \uconcr(\w) = 
  \begin{cases}
    \concr(\w) & \text{if } \forall s \in \PHl, s \subseteq \ctx, \exists \delta \in \concr(\w), \delta \in \Sce(s) \\
    \emptyset & \text{else.}
  \end{cases}
  \]
\end{definition}
% 
\begin{theorem}
\label{th:uconcr-ctx}
  $\ctx \subseteq \ctx' \wedge \muconcr_{\ctx'}(\w) \neq \emptyset \Longrightarrow \muconcr_{\ctx}(\w) \neq \emptyset$.
\end{theorem}

@@

For any objective $P$ and context $\ctx$, \pref{def:maxCont} allows to obtain the set of processes of sort $\PHsort(P)$ that are required to solve $P$ in $\ctx$,
given by $\gCont_\ctx(\PHsort(P), P)$.
\begin{comment}
\begin{definition}
\label{def:allprocs}
  \begin{align*}
  \allprocs(\V, \E) = \{ p \in \PHproc &\mid p \in \V \vee \exists P \in \V \cap \Obj,\\
  &\qquad p = \PHtarget(P) \vee p = \PHbounce(P) \}
%    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \\
%    &\qquad\qquad \vee \exists (a_i,ps) \in \cwRSP, p \in ps \}
  \end{align*}
  \begin{align*}
  \allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \}
  \end{align*}
\end{definition}
\end{comment}
%
\begin{comment}
\begin{definition} \todo{À revoir avec la nouvelle sémantique}
\label{def:allprocs}
  \begin{align*}
  &\allprocs((\cwSol,\cwReq,\cwRSP,\cwCont)) = \{ p \in \PHproc \mid \exists (P,ps) \in \cwSol, \\
    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \\
    &\qquad\qquad \vee \exists (a_i,ps) \in \cwRSP, p \in ps \}
  %  &\qquad\qquad \vee p = \PHtarget(P) \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \\
  %  &\qquad\qquad \vee \exists(Q, \PHobj{p}{\PHbounce(Q)} \in \cwPrioCont \}
  \end{align*}
\end{definition}
\end{comment}
%
%\subsection{Abstract structure}
%
%
\begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \mapsto \powerset(\PHproc)$]
  \label{def:maxCont}
  \begin{align*}
    \gCont_\ctx(a,P) = 
    \{ p \in \PHproc &\mid \exists ps \in \aBS(P), \exists b_i \in ps, b = a \wedge p = b_i \\
      & \vee b \neq a \wedge p \in \gCont_\ctx(a, \PHobj{b_j}{b_i}) \wedge b_j \in \PHget{\ctx}{b} \}
    \enspace.
  \end{align*}
\end{definition}

@@

The reachability of a process $a_i$ is approximated by the ability to solve all objectives $\PHobjp{a}{j}{i}$ so that $a_j$ is in the initial context.
To this end, the abstractions of bounce sequences (\pref{def:aBS}) solving these objectives are computed, leading to new required processes, and thus new objectives in other sorts.
Thus, the graph of local causality $\cwB = (\V, \E)$ defined in \pref{def:glc} is a graph where $\V \subset \Proc \cup \Obj \cup \Sol$ and $\E \subset \V \times \V$
in which edges link any required processes $a_i \in \Proc$ to all corresponding objectives $P \in \Obj$,
and any objective $P$ to abstractions of bounce sequences $ps \in \Sol$ (\pref{def:aBS}) solving this objective;
such sets $ps$ then stand for new required processes.
In the case where a process $a_i$ belongs to a cooperative sort, it is directly linked to the set of the processes $\csState(a_i)$ (\pref{def:csState}) that it represents.
If the solving of an objective $P$ requires a process of $\PHsort(P)$, a continuity edge is added to re-target this objective (\pref{def:maxCont}).
Finally, as the active process of every sort may evolve, the graph $\cwB$ is iteratively saturated by every process it contains,
by overriding its initial context $\ctx$ with $\allprocs(\V, \E)$, defined by:
%in which the initial context $\ctx$ is updated by iteratively adding every process that appears in the graph ($\allprocs$).
%The aim of the this subsection is to build a graph of local causality that describes the propagation of objectives due to the bounce sequence abstraction of \pref{def:aBS}.
%This oriented graph has the form $(\V, \E)$, where $\V \subset \Proc \cup \Obj \cup \Sol$ and $\E \subset \V \times \V$.
%In order to build an accurate under-approximation, this graph is defined as a fixed point, in which each iteration saturates 
%We denote $\allprocs(\V, \E)$ the set of all processes involved in such a graph $(\V, \E)$, defined by: %in \pref{def:allprocs}.
$$\allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \}$$

@@

\begin{definition}
\label{def:glc}
  The graph of local causality $\cwB = (\Bv, \Be)$ is defined as: $\cwB = \lfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
  where $\myB = (\cwV, \cwE)$ is the smallest graph where: $\cwV = \VProc \cup \VObj \cup \VSol$ with $\VProc \subset \PHproc$, $\VObj \subset \Obj$, $\VSol \subset \Sol$ and $\cwE \subset \cwV \times \cwV$ so that:
  \begin{align}
    \w &\subset \cwV \label{eq:Vw} \\
%      \{ \PHbounce(P) \mid P \in \VProc \} &\subset \V\\
    P \in \VProc &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
    (x, y) \in \E &\Rightarrow y \in \cwV \label{eq:VE} \\
%    P \in \VObj &\Rightarrow \PHbounce(P) \in \V\\
%      \{ (P, ps) \in \Obj \times \powerset(\PHproc) \mid P \in \V \wedge ps \in \BS(P) \} &\subset \E\\ % Sol
    P \in \VObj \wedge ps \in \BS(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
%    \{ ps \in \powerset(\PHproc) \mid (P, ps) \in \E \} &\subset \V\\
%      \{ (ps, a_i) \in \powerset(\PHproc) \times \PHproc \mid a_i \in ps \} &\subset \E\\ % Sol
    ps \in \VSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
%    \{ a_i \in \PHproc \mid (ps, a_i) \in \E \} &\subset \V\\
%      \{ (a_i, \PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid a \in \components \wedge a_i \in \V \wedge a_j \in \ctx \} &\subset \E\\ % Req
    a \in \components \wedge a_i \in \VProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
%    \{ \PHobjp{a}{j}{i} \in \Obj \mid (a_i, \PHobjp{a}{j}{i}) \in \E \} &\subset \V\\
%      \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid P \in \V \wedge q \in \gCont_\ctx(\PHsort(P), P) \} &\subset \E\\ % Cont
    P \in \VObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont} \\
%      \{ (a_i, ps) \in \Proc \times \powerset(\PHproc) \mid a \in \cs \wedge a_i \in \V \wedge ps \in \csState(a_i) \} &\subset \E\\ % ReqSolPrio
    a \in \cs \wedge a_i \in \VProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio}
  \end{align}
\end{definition}

\pref{eq:Vw}, \eqref{eq:Vproc} and \eqref{eq:VE} ensure that all required nodes are in $\cwV$.
Elements in $\PHproc$ are required processes,
elements in $\Obj$ are the objectives to reach these processes
and elements in $\Sol$ are the sets of processes that are the solutions to these objectives.
\pref{eq:ESol1} links an objective $P$ to its solutions in $\BS(P)$,
\pref{eq:ESol2} links a solution $ps$ to the processes $a_i \in ps$ it contains and
\pref{eq:EReq} links a required process $a_i$ of a component to all objectives $\PHobjp{a}{j}{i}$ with $a_j \in \ctx$.
If the resolution of an objective $P$ may require a process of $\PHsort(P)$, then \pref{eq:ECont} re-targets this objective ($\gCont$).
Finally, \pref{eq:EPrio} links a required process $a_i$ of a cooperative sorts to its solutions in $\csState(a_i)$.

>>>>

The reachability of a process $a_j$ of a given sort $a$ from another process $a_i$ is called an objective and is denoted $\PHobjp{a}{j}{i}$ (\pref{def:obj}).
\begin{definition}[Objective ($\Obj$)]
\label{def:obj}
  If $a \in \components$, the reachability of a process $a_j$ from a process $a_i$ is called an \emph{objective}, noted $\PHobj{a_i}{a_j}$.
  The set of all objectives is called $\Obj \DEF \{ \PHobj{a_i}{a_j} \mid a \in \components \wedge (a_i, a_j) \in \PHl_a^2 \}$.
  For an objective $P = \PHobj{a_i}{a_j} \in \Obj$, we define: $\PHsort(P) = a$, $\PHtarget(P)=a_i$, $\PHbounce(P)=a_j$,
  and $P$ is \emph{trivial} if $a_i = a_j$.

  We define an \emph{objective sequence} as a sequence of objectives in which each objective target must be equal to the previous objective bounce of the same sort, if it exists.
  The set of all objective sequences is denoted by $\OS$.
\end{definition}

A context (\pref{def:context}) extends the notion of state to a set of possible initial states.
%the extension of the override operator follows (\pref{def:ctxcap}).
We also extend the override operator to contexts (\pref{def:ctxcap}).
\begin{definition}[Context ($\Ctx$)]
\label{def:context}
  A \emph{context} $\ctx$ associates to each sort in $\PHs$ a non-empty subset of its processes:
  $\forall a \in \PHs, \PHget{\ctx}{a} \subseteq \PHl_a \wedge \PHget{\ctx}{a} \neq \emptyset$.
  $\Ctx$ is the set of all contexts.
\end{definition}
%
\begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \rightarrow \Ctx$]
\label{def:ctxcap}
  For any $\ctx\in\Ctx$ and set of processes $ps \in \powerset(\PHproc)$,
  the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by:
  \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} =
  \begin{cases}
    \{ p \in ps \mid \PHsort(p)=a \} & \text{if } \exists p \in ps, \PHsort(p)=a,\\
    \PHget{\ctx}{a} & \text{else.}
  \end{cases}
  \]
\end{definition}
\noindent
For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
$\exists s \subseteq \ctx, \delta \in \Sce(s)$.
We denote then: $\delta \in \Sce(\ctx)$,
%$\supp(\delta) \subseteq \ctx$. 
and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
where $\ceil(\delta)$ is the set containing the last process (hitter or bounce) of each sort present in $\delta$.

@@

Finally, a bounce sequence on a sort $a$ (\pref{def:bs}) is a sequence of actions hitting $a$
in which the bounce process of each action is the hitter process of the following action.
Bounce sequences are used to find local solutions to a given objective.
%Bounce sequences are used to find sequences of actions that locally solve a given objective.
%solve an objective locally, by finding the sequences of actions that allow to reach a process.
A bounce sequence can be abstracted into sets of all its hitters that are not in sort $a$.
%of every action that are different from the considered sort (\pref{def:aBS}).
This abstraction allows to propagate an objective into objectives on other sots.
In the following, we denote: $\Sol = \powerset(\PHproc)$.
\begin{definition}[Bounce sequence ($\BS$)]
\label{def:bs}
  A \emph{bounce sequence} $\zeta$ is a sequence of actions so that $\forall n \in \indexes{\zeta}, n < |\zeta|, \PHbounce(\zeta_{n}) = \PHtarget(\zeta_{n+1})$.
  $\BS$ denotes the set of all bounce sequences, and
  $\BS(P)$ denotes the set of bounce sequences \emph{solving} an objective $P$:
  \[
    \BS(\PHobj{a_i}{a_j}) = \{ \zeta \in \BS \mid \PHtarget(\zeta_1)= a_i \wedge \PHbounce(\zeta_{|\zeta|}) = a_j \} \enspace.
  \]
%  Obviously, $\emptyseq \in \BS(\obj{a_i}{a_i})$; and $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$.
  $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$ and $\emptyseq \in \BS(\obj{a_i}{a_i})$.
\end{definition}
%
\begin{definition}[$\aBS:\Obj \rightarrow \powerset(\Sol)$]
\label{def:aBS}
  \[
    \aBS(P) = \{ \abstr{\zeta} \in \Sol \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \abstr{\zeta'} \subsetneq \abstr{\zeta} \} \enspace,
  \]
  where $\abstr{\zeta} = \{ \PHhitter(\zeta_n) \mid  n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$.
\end{definition}

@@

We define $\concr(\w)$ as the set of scenarios concretising an objective sequence $\w$ in the context $\ctx$.
In \pref{def:uconcr}, we define $\uconcr(\w)$ as equal to $\concr(\w)$ if and only if $\concr(\w)$ contains scenarios starting from all states $s \subseteq \ctx$.
\pref{th:uconcr-ctx} is used to over-approximate the initial context $\ctx$.
%if such a scenario exists in all states $s \subseteq \ctx$.
%
\begin{comment}
\begin{definition}[$\concr: \OS \mapsto \powerset(\Sce)$]
\label{def:concr}
\towrite{Simplifier ? Supprimer la def formelle ?}
  For a given $\w \in \OS$, $\concr(\w)$ is the set of scenarios concretising $\w$ in the context $\ctx$:
  \begin{align*}
    \concr(\w) = \{ \delta \in \Sce \mid & (\w^\vartriangle = \emptyseq \wedge \delta = \emptyseq) 
      \vee (\w^\vartriangle \neq \emptyseq \wedge \supp(\delta) \subseteq \ctx
    \\ &
      \wedge \exists \phi:\indexes{\w} \mapsto \indexes{\delta}, (\forall n, m \in \indexes{\w}, n < m \Leftrightarrow \phi(n) \leq \phi(m)) 
    \\ &
      \wedge \forall n \in \indexes{\w}, \PHbounce(\w_n) \in \ctx \PHplay \delta_{1..\phi(n)})
    \}
    \enspace,
  \end{align*}
  where $\omega^\vartriangle$ refers to the sequence of objectives $\omega$ where the trivial objectives have been removed.
\end{definition}
%
\begin{definition}[$\concr: \powerset(\OS) \mapsto \powerset(\Sce)$]
\label{def:concr-set}
  $\concr(\W) = \{ \delta \in \concr(\w) \mid \w \in \W \} \enspace.$
\end{definition}
\end{comment}
%
\begin{definition}[$\uconcr: \OS \rightarrow \powerset(\Sce)$]
\label{def:uconcr}
  \[
  \uconcr(\w) = 
  \begin{cases}
    \concr(\w) & \text{if } \forall s \in \PHl, s \subseteq \ctx, \exists \delta \in \concr(\w), \delta \in \Sce(s) \\
    \emptyset & \text{else.}
  \end{cases}
  \]
\end{definition}
% 
\begin{theorem}
\label{th:uconcr-ctx}
  $\ctx \subseteq \ctx' \wedge \muconcr_{\ctx'}(\w) \neq \emptyset \Longrightarrow \muconcr_{\ctx}(\w) \neq \emptyset$.
\end{theorem}

@@

For any objective $P$ and context $\ctx$, \pref{def:maxCont} allows to obtain the set of processes of sort $\PHsort(P)$ are required to solve $P$ in $\ctx$, given by $\gCont_\ctx(\PHsort(P), P)$.
\begin{comment}
\begin{definition}
\label{def:allprocs}
  \begin{align*}
  \allprocs(\V, \E) = \{ p \in \PHproc &\mid p \in \V \vee \exists P \in \V \cap \Obj,\\
  &\qquad p = \PHtarget(P) \vee p = \PHbounce(P) \}
%    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \\
%    &\qquad\qquad \vee \exists (a_i,ps) \in \cwRSP, p \in ps \}
  \end{align*}
  \begin{align*}
  \allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \}
  \end{align*}
\end{definition}
\end{comment}
%
\begin{comment}
\begin{definition} \todo{À revoir avec la nouvelle sémantique}
\label{def:allprocs}
  \begin{align*}
  &\allprocs((\cwSol,\cwReq,\cwRSP,\cwCont)) = \{ p \in \PHproc \mid \exists (P,ps) \in \cwSol, \\
    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \\
    &\qquad\qquad \vee \exists (a_i,ps) \in \cwRSP, p \in ps \}
  %  &\qquad\qquad \vee p = \PHtarget(P) \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \\
  %  &\qquad\qquad \vee \exists(Q, \PHobj{p}{\PHbounce(Q)} \in \cwPrioCont \}
  \end{align*}
\end{definition}
\end{comment}
%
%\subsection{Abstract structure}
%
%
\begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \rightarrow \powerset(\PHproc)$]
  \label{def:maxCont}
  \begin{align*}
    \gCont_\ctx(a,P) = 
    \{ p \in \PHproc &\mid \exists ps \in \aBS(P), \exists b_i \in ps, b = a \wedge p = b_i \\
      & \vee b \neq a \wedge p \in \gCont_\ctx(a, \PHobj{b_j}{b_i}) \wedge b_j \in \PHget{\ctx}{b} \}
    \enspace.
  \end{align*}
\end{definition}

@@

The reachability of a process $a_i$ is approximated by the ability to solve all objectives $\PHobjp{a}{j}{i}$ so that $a_j$ is in the initial context.
To this end, the abstractions of bounce sequences (\pref{def:aBS}) solving these objectives are computed, leading to new required processes, and thus new objectives on other sorts.
Thus, the graph of local causality $\cwB = (\V, \E)$ defined in \pref{def:glc} is a graph where $\V \subset \Proc \cup \Obj \cup \Sol$ and $\E \subset \V \times \V$
in which edges link any required process $a_i$ in $\Proc$ to all corresponding objectives $P$ in $\Obj$,
and any objective $P$ to abstractions of bounce sequences $ps \in \Sol$ (\pref{def:aBS}) solving this objective;
such sets $ps$ then stand for new required processes.
In the case where a process $a_i$ belongs to a cooperative sort, it is directly linked to the set of the processes $\csState(a_i)$ (\pref{def:csState}) that it represents.
If the solving of an objective $P$ requires a process of $\PHsort(P)$, a continuity edge is added to re-target this objective (\pref{def:maxCont}).
Finally, as the active process of every sort may evolve, $\cwB$ is obtained iteratively by saturation with every process it contains,
\ie by overriding its initial context $\ctx$ by $\allprocs(\V, \E)$, defined by:
%in which the initial context $\ctx$ is updated by iteratively adding every process that appears in the graph ($\allprocs$).
%The aim of the this subsection is to build a graph of local causality that describes the propagation of objectives due to the bounce sequence abstraction of \pref{def:aBS}.
%This oriented graph has the form $(\V, \E)$, where $\V \subset \Proc \cup \Obj \cup \Sol$ and $\E \subset \V \times \V$.
%In order to build an accurate under-approximation, this graph is defined as a fixed point, in which each iteration saturates 
%We denote $\allprocs(\V, \E)$ the set of all processes involved in such a graph $(\V, \E)$, defined by: %in \pref{def:allprocs}.
$$\allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \}$$

@@

\begin{definition}
\label{def:glc}
  The graph of local causality $\cwB = (\Bv, \Be)$ is defined as: $\cwB = \lfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
  where $\myB = (\cwV, \cwE)$ is the smallest graph where:
  %$\cwV = \VProc \cup \VObj \cup \VSol$ with $\VProc \subset \PHproc$, $\VObj \subset \Obj$, $\VSol \subset \Sol$ and $\cwE \subset \cwV \times \cwV$
  $\cwV \subset \Proc \cup \Obj \cup \Sol$ and $\cwE \subset \cwV \times \cwV$
  so that:
  \begin{align}
    \w &\subset \cwV \label{eq:Vw} \\
%      \{ \PHbounce(P) \mid P \in \VProc \} &\subset \V\\
    P \in \VProc &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
    (x, y) \in \E &\Rightarrow y \in \cwV \label{eq:VE} \\
%    P \in \VObj &\Rightarrow \PHbounce(P) \in \V\\
%      \{ (P, ps) \in \Obj \times \powerset(\PHproc) \mid P \in \V \wedge ps \in \BS(P) \} &\subset \E\\ % Sol
    P \in \VObj \wedge ps \in \BS(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
%    \{ ps \in \powerset(\PHproc) \mid (P, ps) \in \E \} &\subset \V\\
%      \{ (ps, a_i) \in \powerset(\PHproc) \times \PHproc \mid a_i \in ps \} &\subset \E\\ % Sol
    ps \in \VSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
%    \{ a_i \in \PHproc \mid (ps, a_i) \in \E \} &\subset \V\\
%      \{ (a_i, \PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid a \in \components \wedge a_i \in \V \wedge a_j \in \ctx \} &\subset \E\\ % Req
    a \in \components \wedge a_i \in \VProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
%      \{ (a_i, ps) \in \Proc \times \powerset(\PHproc) \mid a \in \cs \wedge a_i \in \V \wedge ps \in \csState(a_i) \} &\subset \E\\ % ReqSolPrio
    a \in \cs \wedge a_i \in \VProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio} \\
%    \{ \PHobjp{a}{j}{i} \in \Obj \mid (a_i, \PHobjp{a}{j}{i}) \in \E \} &\subset \V\\
%      \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid P \in \V \wedge q \in \gCont_\ctx(\PHsort(P), P) \} &\subset \E\\ % Cont
    P \in \VObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont}
  \end{align}
\end{definition}

\pref{eq:Vw}, \eqref{eq:Vproc} and \eqref{eq:VE} ensure that all required nodes are in $\cwV$.
Elements in $\PHproc$ are required processes,
elements in $\Obj$ are the objectives to reach these processes
and elements in $\Sol$ are the sets of processes that allow to solve these objectives.
\pref{eq:ESol1} links an objective $P$ to its solutions in $\BS(P)$
and \pref{eq:ESol2} links a solution $ps$ to the processes $a_i \in ps$ it contains.
Then, \pref{eq:EReq} links a required component process $a_i$ to all objectives $\PHobjp{a}{j}{i}$ with $a_j \in \ctx$
while \pref{eq:EPrio} links a required cooperative sort process $a_i$ to its solutions in $\csState(a_i)$.
Finally, if the resolution of an objective $P$ requires a process of $\PHsort(P)$, then \pref{eq:ECont} re-targets this objective ($\gCont$).

%In the following, we denote:
%$\BvProc = \Bv \cap \PHproc$, $\BvObj = \Bv \cap \Obj$ and $\BvSol = \Bv \cap \Sol$.
%$\Bee{X}{Y} = \Be \cap (X \times Y)$, with $X, Y$ amongst $\PHproc$, $\Obj$ and $\Sol$.
%
\begin{comment}
\begin{definition}
  \label{def:aS}
  The abstract structure $\cwB=(\Breq,\Bsol,\Brsp,\Bcont)$ is defined as
  $\cwB = \sfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}$,\\
  with $\myB=(\myreq,\mysol,\myrsp,\mycont)$:
  \begin{align*}
    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
      a \in \components \wedge a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
      & \qquad \wedge ((\exists (P,ps) \in \mysol \vee \exists (b_j, ps) \in \myrsp), a_i \in ps \\
      & \qquad\qquad \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
    \\
    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
      & \qquad\qquad \vee \exists (Q, P) \in \mycont \wedge ps \in \aBS(P) \}
    \\
    \myrsp &= \{ (a_i,ps) \in \PHproc \times \powerset(\PHproc) \mid a \in \cs \\
      & \qquad \wedge (\exists (P,ps') \in \mysol \vee \exists (b_j,ps') \in \myrsp), \\
      & \qquad\qquad a_i \in ps' \wedge \csState(a_i) \in ps \}
    \\
    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
      \exists (P, ps) \in \mysol \\
      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
  \end{align*}
\end{definition}
